Edge sign prediction in general graphs and Correlation Clustering

### 2017-11-21 intro/main.tex
say complex networks have 2 features: k edge types and homo/hetero mix

At this point of the discussion though, we have only considered the most common and simple kind of
graph, one representing a single type of relation between nodes. However, in many situations, nodes
have more than one type of relation among each other. As a case in point, let us look again at our
three examples. In the \wik{} network, a vote can support the promotion or oppose it. This
additional information enrich our understanding of the relationships between the nodes in the graph.
Likewise in an image, an edge between two pixels is positive if the two pixels belong to the same
object (say a car or a building) and negative otherwise. Such information could be used to segment
the image. In the co-purchase network, there is even more than two types of relation. Assuming the
products are movies, two movies can be frequently bought together because they are part of a series
(like Star Wars), because they have the same director, because they receive the same prestigious
awards in different years, and so on. In \autoref{sec:edge_semantics}, we give additional examples
of so-called \emph{complex networks}, where edges have different \emph{semantics}, or types. As
showed in our examples, we distinguish between two cases. The first is when there are two types of
edge having opposite semantics. Such graphs are called \emph{signed graphs} and have been
extensively studied since the fifties, for we shall see they have many applications. The second case
is when there are more than two types of edge. Such graphs have also been studied for a long time
under different names and we refer to them as \emph{multilayer graphs}.

It is natural to expect that we can extract finer insights from graphs with edge semantics. However,
in many cases, the information about edge types is not available. We therefore present in
\autoref{sec:predicting_edge_type} the problem of characterizing edges in complex networks.
Informally, given an input graph and possibly some extra information, we want to predict the type of
every edge. This problem can take several forms depending of what information is available as input.
First, the graph may be directed or undirected. Second, there might be two edge types (in the case of
signed graphs) or more (for general multilayer graphs). Third, the problem can be supervised or not.
In the supervised setting, we are provided with labels for some of the edges. In the unsupervised
setting, there is no label. We thus make the additional assumption that we observe the
\emph{attributes} of the nodes. Once again, we return to our three examples to illustrate what are
those attributes. In the \wik{} graph, we could have for each user data about age, experience and
area of expertise. In an image, each pixel is associated with a color, along with higher order
visual features. Each product of a co-purchase network comes with information about \eg{}, its price,
popularity, category and availability. In the absence of label, our intuition is that these
attributes can inform us about the type of edge between nodes.

>>>>

\medskip

At this point of the discussion though, we have only considered the most common and simple kind of
graph, one representing a single type of relation between nodes. However, in many situations, there
are two dimensions along which graphs exhibit more complexity. First, nodes have more than one type
of relation among each other. Second, two nodes are not only connected because of their global
similarity but also for more nuanced reasons. As a case in point, let us look again at our
three examples. In the \wik{} network, a vote can support the promotion or oppose it. This
additional information enrich our understanding of the relationships between the nodes in the graph.
It also points out that two editors can be connected because they share a common topic of interest,
but come from different socio-economic backgrounds and therefore cannot agree on this topic.
Likewise in an image, an edge between two pixels is positive if the two pixels belong to the same
object (say a car or a building) and negative otherwise. This information could be used to segment
the image. In the co-purchase network, there are even more than two types of relation. Assuming the
products are movies, two movies can be frequently bought together because they are part of a series
(like Star Wars), because they have the same director but different gender, because they receive the
same prestigious awards in different years, and so on. The second type of relation (\enquote{same
director} and \enquote{different gender}) is actually an example of a mixed relation, for it mixes
similarity and dissimilarity.

We call \emph{complex networks} graphs where edges have different \emph{semantics}, or types, and
where connections are explained by more than simple global similarity. In
\autoref{sec:edge_semantics}, we give additional examples of such complex networks. As
showed in our three previous examples, we distinguish between two cases. The first is when there are two types of
edge having opposite semantics. Such graphs are called \emph{signed graphs} and have been
extensively studied since the fifties, for we shall see they have many applications. The second case
is when there are more than two types of edge. Such graphs have also been studied for a long time
under different names and we refer to them as \emph{multilayer graphs}.

\medskip

It is natural to expect that we can extract finer insights from graphs with edge semantics. However,
in many cases, the information about edge types is not available. We therefore present in
\autoref{sec:predicting_edge_type} the problem of characterizing edges in complex networks.
Informally, given an input graph and possibly some extra information, we want to predict the type of
every edge. This problem can take several forms depending of what information is available as input.
First, the graph may be directed or undirected. Second, there might be two edge types (in the case of
signed graphs) or more (for general multilayer graphs). Third, the problem can be supervised or not.
In the supervised setting, we are provided with labels for some of the edges. In the unsupervised
setting, there is no label at all. We thus make the additional assumption that we observe some
\emph{attributes} of the nodes. Once again, we return to our three examples to illustrate what
those attributes can be. In the \wik{} graph, we could have for each user data about age, experience and
area of expertise. In an image, each pixel is associated with a color, along with higher order
visual features. Each product of a co-purchase network comes with information about, \eg{}, its price,
popularity, category and availability. In the absence of label, our intuition is that these
attributes can inform us about the type of edge between nodes.

\medskip
